\section{User Characteristics}
The actors of the applications are the following:
\begin{itemize}
    \item \textit {Unregistered user}: a person who has not yet registered and is only allowed to sign up becoming either a Policy maker or an Agronomist or a Farmer depending on the type of role selected.
    \item \textit {User}: a person who is already registered into the application and is allowed to sign in according to his/her role (Policy maker, Agronomist, Farmer).
    \item \textit {Policy maker}: a user of DREAM. He/She is an institutional figure in the public or private sector who has the power to elaborate and determine guidelines and strategies on the most relevant issues for society and politics. 
    \item \textit {Agronomist}: a user of DREAM. He/She is a multidisciplinary professional figure. He/She works in favor of farms and small farmers by analyzing and developing projects based on direct observation and on the study of the best environmental solutions in order to improve productivity and enhance agricultural products.
    \item \textit {Farmer}: a user of DREAM. He/She is the figure who deals with managing, carrying out and producing crops of different kinds and types, constantly taking care of their good health. Furthermore, the farmer ensures that the places where the cultivation takes place fully comply with the hygienic-sanitary rules of the cultivation. They also provide for the maintenance of the structures necessary for the activities and the reclamation of the environments in which the cultivation takes place.

\end{itemize}